Møil: A web-based administration tool for mail servers backed by relational databases

### 2014-07-24 doc/paper/paper.tex
Started evaluation and added info table for solutions.

	\section*{Abstract}
		This document compares existing administration user interface solutions
		for mail servers backed by relational databases and introduces yet
		another one, which is called Møil and is written in Ruby utilizing the
		Ruby on Rails\footnote{\url{http://rubyonrails.org}} framework. It
		brings the handy possibility of managing the database schema with
		migrations, a lot of beautiful, responsive CRUD and some other nice
		features (see page \pageref{moeil-features}). The code is available from
		GitHub\footnote{\url{https://github.com/nning/moeil}} under the AGPLv3
		\cite{agpl}.

	\section*{Introduction}
		For mail system setups (meaning one or more servers running Mail
		Submission, Delivery and Transfer Agent software and providing a
		Message Store for users \cite{mail-architecture}), storing data about
		which domains and E-Mail addresses the system is responsible for
		(further called meta data) in relational databases (as opposed to plain
		files for example) is beneficial for several reasons.

		% Reasons for database-backing
		%	Horizontal scalability

		In bigger setups, it offers the possibility for scaling to more than
		one node (horizontal scalability) to cope with high mail and user
		loads: Several servers handling incoming mail or users reading their
		mail act as readers on one or more database servers. The performance of
		the frequent lookups of domains, mailboxes and aliases (forwardings)
		for receiving mail or user logins can be increased. (We can not
		consider another big problem with horizontal scaling of Message Stores,
		here -- the actual accommodation of E-Mails.)

@@

@@

		\subsection*{The contestants}
			% PHP
			%	ratuus http://www.ratuus.org/
			%	ViMbAdmin http://www.vimbadmin.net/
			%	postfix.admin http://postfixadmin.sourceforge.net/
			% Perl
			%	VBox.Adm http://www.vboxadm.net/
			% Python
			%	modoboa http://modoboa.org

	\section*{A new solution: Møil}
		% Rails
		% Causes for a new solution
		%	Data model, migrations
		%	CLI
		%	Password hash generation for compatibility to older solution
		%	Other features

>>>>

	\section*{Abstract}
		This document compares existing administration user interface solutions
		for mail servers backed by relational databases and introduces yet
		another one, which is called Møil and is written in Ruby utilizing the
		Ruby on Rails\footnote{\url{http://rubyonrails.org}} framework. It
		brings the handy possibility of managing the database schema with
		migrations, a lot of beautiful, responsive CRUD and some other nice
		features (see page \pageref{moeil-features}). The code is available from
		GitHub\footnote{\url{https://github.com/nning/moeil}} licensed under
		AGPLv3 \cite{agpl}.

	\section*{Introduction}
		% Reasons for database-backing

		For mail system setups (meaning one or more servers running Mail
		Submission, Delivery and Transfer Agent software and providing a
		Message Store for users \cite{mail-architecture}), storing data about
		which domains and E-Mail addresses the system is responsible for
		(further called meta data) in relational databases (as opposed to plain
		files for example) is beneficial for several reasons.

		%	Horizontal scalability

		In bigger setups, it offers the possibility for scaling to more than
		one node (horizontal scalability) to cope with high mail and user
		loads: Several servers handling incoming mail or users reading their
		mail act as readers on one or more database servers. The performance of
		the frequent lookups of domains, mailboxes and aliases (forwardings)
		for receiving mail or user logins can be increased. (The actual
		accommodation of E-Mails -- another big problem with horizontal scaling
		-- can not be considered here.)

@@

		Although an extensive evaluation of the existing administration user
		interfaces did not happen before implementing a custom solution, some
		of the programs were still sighted and some of the following criteria
		was still considered. This more systematical and detailed analysis
		shall gain an overview and provide inspiration for the development of
		Møil.

@@

		\subsection*{The contestants}
			\subsubsection*{modoboa}
				\infotable{http://modoboa.org}{Python}

			\subsubsection*{postfix.admin}
				\infotable{http://postfixadmin.sourceforge.net}{PHP}

			\subsubsection*{ratuus}
				\infotable{http://www.ratuus.org}{PHP}

			\subsubsection*{VBox.Adm}
				\infotable{http://www.vboxadm.net}{Perl}

			\subsubsection*{ViMbAdmin}
				\infotable{http://www.vimbadmin.net}{PHP}

	\section*{Møil}
		% Rails
		% Causes for a new solution
		%	Data model, migrations
		%	CLI
		%	Password hash generation for compatibility to older solution
		%	Other features
